Network visualizations

### 2024-02-21 scripts/02.1_visualizeNetworks.qmd
updates to graphs

# Have to join `linked` back to `networkMetrics` so we maintain the network values for those that don't ultimately get included in movement
info <- networkMetrics %>%
  left_join(linked %>%
              select(Nili_id, "season" = seasonUnique, daysTracked, propDaysTracked, birth_year, sex, space_use, movement, roost_div, space_use_log, age, age_group, type)) %>%
  mutate(focal = case_when(is.na(movement) & is.na(space_use) & is.na(roost_div) ~ FALSE,
                           TRUE ~ TRUE))
nrow(info) == nrow(networkMetrics) # TRUE
nrow(linked) < nrow(info) # TRUE

@@

```{r}
# Network visualizations ----------------------------------------------------------------
grph_deg <- function(graph, season_name, type){
  g <- graph %>%
    ggraph(layout = "fr")+
    geom_edge_link(alpha = 0.2)+
    geom_node_point(aes(size = normDegree, col = normDegree))+
    scale_color_viridis()+
    theme(legend.position = "none")+
    ggtitle(season_name)
  return(g)
}

grph_str <- function(graph, season_name, type){
  g <- graph %>%
    ggraph(layout = "fr")+
    geom_edge_link(alpha = 0.2)+
    geom_node_point(aes(size = normStrength, col = normStrength))+
    scale_color_viridis()+
    theme(legend.position = "none")+
    ggtitle(season_name)
  return(g)
}

flightPlots_degree <- map2(.x = flightGraphs, .y = season_names, ~grph_deg(.x, .y, type = "flight"))
feedingPlots_degree <- map2(.x = feedingGraphs, .y = season_names, ~grph_deg(.x, .y, type = "feeding"))
roostingPlots_degree <- map2(.x = roostingGraphs, .y = season_names, ~grph_deg(.x, .y, type = "roosting"))

>>>>

# Have to join `linked` back to `networkMetrics` so we maintain the network values for those that don't ultimately get included in movement
info <- networkMetrics %>%
  left_join(linked %>%
              select(Nili_id, "season" = seasonUnique, daysTracked, propDaysTracked, birth_year, sex, space_use, movement, roost_div, space_use_log, age, age_group, type)) %>%
  mutate(focal = case_when(is.na(movement) & 
                             is.na(space_use) & 
                             is.na(roost_div) ~ FALSE,
                           TRUE ~ TRUE),
         label = case_when(!focal ~ Nili_id,
                           TRUE ~ NA_character_))
nrow(info) == nrow(networkMetrics) # TRUE
nrow(linked) < nrow(info) # TRUE

@@

```{r}
#| message: false
# Network visualizations ----------------------------------------------------------------
grph_deg <- function(graph, season_name, type){
  g <- graph %>%
    ggraph(layout = "fr")+
    geom_edge_link(alpha = 0.2)+
    geom_node_point(aes(size = normDegree, col = normDegree, shape = dataset))+
    geom_node_text(aes(label = label,
                       hjust = -0.2, vjust = 0.1))+
    scale_shape_manual(name = "Focal", values = c(17, 16))+
    scale_color_viridis()+
    theme(legend.position = "none")+
    ggtitle(season_name)
  return(g)
}

grph_str <- function(graph, season_name, type){
  g <- graph %>%
    ggraph(layout = "fr")+
    geom_edge_link(alpha = 0.2)+
    geom_node_point(aes(size = normStrength, 
                        col = normStrength, 
                        shape = dataset))+
    geom_node_text(aes(label = label,
                       hjust = -0.2, vjust = 0.1))+
    scale_shape_manual(name = "Focal", values = c(17, 16))+
    scale_color_viridis()+
    theme(legend.position = "none")+
    ggtitle(season_name)
  return(g)
}

grph_test <- function(graph, season_name, type){
  g <- graph %>%
    ggraph(layout = "fr")+
    geom_edge_link(alpha = 0.2)+
    geom_node_point(aes(size = normStrength, 
                        col = normStrength, 
                        shape = focal))+
    geom_node_text(aes(label = label,
                       hjust = -0.2, vjust = 0.1))+
    scale_shape_manual(name = "Focal", values = c(17, 16))+
    scale_color_viridis()+
    theme(legend.position = "none")+
    ggtitle(season_name)
  return(g)
}

grph_test(flightGraphs[[2]], "2021_breeding", type = "flight")
```

```{r}
flightPlots_degree <- map2(.x = flightGraphs, .y = season_names, ~grph_deg(.x, .y, type = "flight"))
feedingPlots_degree <- map2(.x = feedingGraphs, .y = season_names, ~grph_deg(.x, .y, type = "feeding"))
roostingPlots_degree <- map2(.x = roostingGraphs, .y = season_names, ~grph_deg(.x, .y, type = "roosting"))
